---
title: "Linear Regression"
author: "Kerrie Stewart"
output: github_document
---

```{r}
eclsk <- read.csv("eclsk.csv")
```


```{r}
library(rstanarm)
library(rstan)
```

## Regression Model
  
```{r}
Model <- stan_glm(read ~ female, data=eclsk)
```

```{r}
summary(Model)
```
## R Squared

```{r}
r_squared_post <- bayes_R2(Model)
```

```{r}
mean_r_squared <- mean(r_squared_post)
```

```{r}
print(mean_r_squared)
```



## Scatterplot


```{r}
plot(eclsk$female, eclsk$read, 
     xlab = "Female", ylab = "Reading Score", 
     main = "Reading Score vs. Female", 
     pch = 19, col = "blue", 
     xaxt = "n") 
abline(Model, col = "red", lwd = 2)
```

## Plot with Equation

```{r}
intercept <- coef(Model)[1]
coefficient <- coef(Model)[2]
```

```{r}
equation <- paste("y = ", round(intercept, 2), " + ", round(coefficient, 2), "x", sep = "")
```

```{r}
plot(eclsk$female, eclsk$read, 
     xlab = "Female", ylab = "Reading Score", 
     main = "Reading Score vs. Female", 
     pch = 19, col = "blue", 
     xaxt = "n") 
abline(Model, col = "red", lwd = 2)
text(0.5, 50, labels = equation, col = 'green', cex = 1.2)
```

## Interpretation

The model estimates the relationship between gender and reading scores. y is the reading score (dependent variable). Gender is measured as a binary variable where students are coded as either female (1) or not female (0). The intercept, the reading score for a student who is not female, is predicted to be 48.83. The slope (-2.36)  indicates that being female is associated with a decrease of 2.36 points in the reading score, on average, compared to students who are not female. This model suggests that female students have lower reading scores, on average , than non-female students. The R squared value is 0.0072 indicating that only 0.72% of the variance in reading scores is explained by whether a student is female or not. This low R squared suggests that gender is not a predictor of reading scores, or this model is not a good fit.


